\documentclass{article}
\usepackage{calc}
\usepackage[top=0.5in,bottom=0.63in,right=0.75in,left=0.75in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontenc}
\usepackage{tgbonum}
\usepackage{subfiles}
\usepackage{titlesec} 
\usepackage{multicol}

\pretolerance=10000
\tolerance=2000
\emergencystretch=10pt

\titlespacing*{\section}{0pt}{1\baselineskip}{0.2\baselineskip}

\setlist[enumerate]{topsep=0pt}
\setlist[itemize]{noitemsep,topsep=0pt}

\newlength{\remaining}
\renewcommand{\section}[1]{%
  \vspace{0.4em}\setlength{\remaining}{\textwidth-\widthof{\uppercase{#1}}}
    \noindent\underline{\fontsize{8}{12}\bfseries\uppercase{#1}\hspace*{\remaining}} \\
}
\renewcommand{\subsection}[3]{
    \noindent\textbf{#1} | \emph{#2} \hfill #3
}
\newcommand{\subsectionedu}[3]{
	\noindent\textbf{#1}  \emph{#2} \hfill #3 \break
}
\pagenumbering{gobble}

\begin{document}
    \fontencoding{T1}
    \fontfamily{phv}
    \fontsize{8}{12}
    \selectfont
    \begin{center}
        \begin{center}
            \Huge\bfseries Marcin Rolbiecki
            \vspace{1em}
        \end{center}
            \begin{tabular}{c c cc}
                \href{tel:+48 512 540 840}{+48 512 540 840} $\bullet$ & 
                \href{mailto:rolbieckidev@gmail.com}{rolbieckidev@gmail.com} $\bullet$ & 
                \href{https://www.linkedin.com/in/mrolbiecki/}{linkedin/mrolbiecki} $\bullet$ & 
                \href{https://github.com/mrolbiecki/}{github/mrolbiecki}
        \end{tabular}
        \vspace{1em}
    \end{center}    
    \vspace{-0.75em}

	\section{Education}
	\subsectionedu{University of Warsaw - Faculty of Mathematics, Informatics and Mechanics}{}{Oct 2023 - Expected Jun 2026}
	BSc in Computer Science, Warsaw, Poland \hfill

	\begin{itemize}
		\item \textbf{Relevant coursework:} Concurrent Programming (Distributed and Parallel Systems), Databases, Object-Oriented Programming, Computer Architecture, Operating Systems, Algorithms and Data Structures.
		\item \textbf{Upcoming by Internship Start:} Machine Learning, Web Application Development.
	\end{itemize}

	\vspace{0.75em}

    \section{Experience}
    \subsection{Junior Software Developer}{Atinea}{Jun 2024 - Present}
    \begin{itemize}
        \item Developed database web application using \textbf{MySQL} on \textbf{Linux} environment.
        \item Learned NianioLang within 1 week, showcasing ability to learn new programming languages as needed by project requirements.
        \item Improved the efficiency of complex \textbf{SQL} query execution by reducing time complexity through the application of graph algorithms and advanced data structures, resulting in better scalability and performance.
    \end{itemize}
	\vspace{0.5em}

    \subsection{Problemsetter}{Instakod}{Jun 2022 - Present}
    \begin{itemize}
        \item Designed problems for "Instalogik", an annual math and programming contest, driving engagement in STEM education for primary school students.
        \item Contributed to a 35\% increase in participation in the second year, growing from 9K to 12K+ students.
    \end{itemize}
    \vspace{0.5em}

    \subsection{Computer Science Tutor}{Instakod, IT korepetycje}{Apr 2022 - Aug 2024}
    \begin{itemize}
        \item Delivered tutoring sessions in \textbf{C++} and \textbf{Python}, focusing on algorithms and programming contests preparation for 20+ students.
    \end{itemize}
    
    \vspace{0.75em}

    \section{Personal Projects and Certifications}
    \subsection{University Projects}{University of Warsaw}{Oct 2023 - Present}
    \begin{itemize}
        \item Parallelized solution in \textbf{C} using \textbf{pthreads} for a combinatorial problem, focusing on \textbf{scalability} for a large number of threads. \href{https://github.com/mrolbiecki/university-projects/tree/main/concurrent-programming/parallel-combinatorics}{github link}.
        \item \textbf{C} library for performing arithmetic operations on approximate values. \href{https://github.com/mrolbiecki/university-projects/tree/main/introductory-programming/arithmetic-of-approximate-values}{github link}.
        \item \textbf{Concurrent} boolean circuit solver in \textbf{Java}, enabling parallel evaluation of complex boolean expressions. \href{https://github.com/mrolbiecki/university-projects/tree/main/concurrent-programming/circuit-solver}{github link}.
        \item Data analysis project in \textbf{Python}, leveraging \textbf{pandas} and \textbf{matplotlib} to process and visualize DrugBank data. \href{https://github.com/mrolbiecki/university-projects/tree/main/python-course/data-analysis}{github link}.
    \end{itemize}
    \vspace{0.5em}

    \subsection{Algorithms and Data Structures Solutions}{}{Aug 2021 - Present}
    \begin{itemize}
        \item Solved over 500 complex problems during live contests or training. \href{https://github.com/mrolbiecki/competitive-programming-solutions}{github link}.
    \end{itemize}
    \vspace{0.5em}
    
    \subsection{NVIDIA Fundamentals of Deep Learning}{Remote}{Aug 2024}
    \begin{itemize}
        \item Completed a workshop on deep learning fundamentals, utilizing the \textbf{PyTorch} library to train neural networks for solving real-world challenges in \textbf{computer vision} and \textbf{natural language processing}.
    \end{itemize}
    
    \vspace{0.75em}

    \section{Achievements}
    \subsection{Finalist of Polish Olympiad in Informatics}{Warsaw}{Mar 2023}
    \begin{itemize}
        \item Ranked in the top 100 out of over 1,400 participants from the best Polish high schools, demonstrating advanced problem-solving skills in algorithms and data structures.
    \end{itemize}
    
    \vspace{0.75em}

    \section{Leadership / Activities}
    \subsection{Assistant Unit Leader}{Związek Harcerstwa Rzeczypospolitej (Boy Scouts), Bytów}{Mar 2021 - Present}
    \begin{itemize}
        \item Co-organized multiple large-scale events, including 3 summer camps for over 100 participants, each lasting 4 weeks, enhancing team collaboration and social skills.
        \item Led and coordinated groups of 20+ members, planning and executing complex tasks such as setting up campsites, demonstrating strong organizational and leadership abilities.
    \end{itemize}

    \subsection{Volunteering}{Various Charities}{}
    \begin{itemize}
        \item Regularly involved in charity work, including assisting with local charity events in my hometown and participating in high-impact initiatives, such as supporting refugees at the Polish-Ukrainian border during a humanitarian crisis.
    \end{itemize}
    
    \vspace{0.75em}

    \section{Skills}
    \vspace{-1em}
    \begin{multicols}{2}
        \subsection{Tools and Technologies}{}{}
        \begin{itemize}
            \item Linux, Git, Office, MySQL, PostgreSQL, LaTeX.
        \end{itemize}

        \subsection{Languages}{}{}
        \begin{itemize}
            \item Polish (Native), English (C1), German (A2).
        \end{itemize}

        \subsection{Programming Languages}{}{}
        \begin{itemize}
            \item C++, C, Python, SQL, Java, Bash.
            \item Quick at learning new languages as required by project needs.
        \end{itemize}
    \end{multicols}
\end{document}
